% By Abdullah As-Sadeed

\documentclass[
	a4paper,
	12pt,
]{resume}

\usepackage[none]{hyphenat}
\usepackage{longtable}
\usepackage{multicol}

\name{Abdullah As-Sadeed}

\address{xxxx xxxxxxxxxx, xxx xxxxx, xxxxxxxxxxx, Dhaka xxxx}

\address{(880)~$\cdot$~xxxx~$\cdot$~xxxxxx \\ sadeed@iut-dhaka.edu}

\begin{document}

\begin{rSection}{Career Objective}

	Passionate Technology Management graduate committed to research and teaching future technology leaders, aiming to bridge business and open-source technologies with a strong focus on cybersecurity.

\end{rSection}


\begin{rSection}{Education}

	\textbf{Institute of Cost and Management Accountants of Bangladesh} \hfill \textit{} \\
	Certified Management Accountant \\
	Passed: Knowledge Level \\
	Session: January - June 2026

	\textbf{Islamic University of Technology, OIC} \hfill \textit{} \\
	BBA in Technology Management \\
	Department of Business and Technology Management \\
	CGPA: 3.83 on a 4 point scale \\
	Merit Position: 3\textsuperscript{rd} (Tied) \\
	Year of Passing: 2025

	\textbf{Dhaka City College} \hfill \textit{} \\
	Higher Secondary Certificate (Science Group) \\
	Board of Intermediate and Secondary Education, Dhaka \\
	GPA: 5.00 on a 5 point scale \\
	Year of Passing: 2020

	\textbf{Faizur Rahman Ideal Institute} \hfill \textit{} \\
	Secondary School Certificate (Science Group) \\
	Board of Intermediate and Secondary Education, Dhaka \\
	GPA: 5.00 on a 5 point scale \\
	Year of Passing: 2018

	\textbf{Faizur Rahman Ideal Institute} \hfill \textit{} \\
	Junior School Certificate \\
	Board of Intermediate and Secondary Education, Dhaka \\
	GPA: 5.00 on a 5 point scale \\
	Year of Passing: 2015

\end{rSection}

\begin{rSection}{Certification}

	\textbf{IBM Cybersecurity Analyst} \hfill \textit{} \\
	August, 2025

	\textbf{Microsoft Cybersecurity Analyst} \hfill \textit{} \\
	August, 2025

\end{rSection}

\begin{rSection}{Research}

	\textbf{The Cost-Effectiveness of Shoplifting Prediction Using 3D CNN for Retailers} \hfill \textit{} \\
	Ongoing \\

\end{rSection}

\begin{rSection}{Experience}

	\begin{rSubsection}{AlmaLinux OS Foundation}{July 2022 - Present}{Member}{California, USA}
		\item Code Contributor
		\item Member, Election Committee, Board of Directors Election 2023
	\end{rSubsection}

	\begin{rSubsection}{AkijBashir Group}{February 2025 - May 2025}{Flutter Developer (Information Technology Intern)}{Dhaka, Bangladesh}
		\item Developed multiple file uploader and downloader and implemented iOS compatibility for their employee support system application and a retailer campaign application.
		\item Developed a facial attendance application for tea estate workers to a testable extent, along with Bluetooth weight scale functionality.
		\item Developed an Ollama application to a testable extent, intended as a support chat for the retailer campaign applications.
		\item Led the migration of APIs for another retailer campaign program application.
		\item Enrolled an Apple Developer account for the group.
	\end{rSubsection}

\end{rSection}

\begin{rSection}{Project}

	\begin{rSubsection}{Bitscoper CyberKit}{}{Personal Open-Source Project}{}
		\item A cross-platform Flutter application offering IPv4 Subnet Scanner, mDNS Scanner, TCP Port Scanner, Route Tracer, Pinger, File Hash Calculator, String Hash Calculator, CVSS Calculator, Base Encoder, Morse Code Translator, QR Code Generator, Open Graph Protocol Data Extractor, Series URI Crawler, DNS Record Retriever, WHOIS Retriever, and Wi-Fi Information Viewer.
		\item Available on Microsoft Store, Google Play, GitHub Container Registry (GHCR), and Amazon Elastic Container Registry (ECR) Public Gallery.
	\end{rSubsection}

	\begin{rSubsection}{Bitscoper IoT}{}{Personal Open-Source Project}{}
		\item A versatile Internet of Things project.
	\end{rSubsection}

	\begin{rSubsection}{TeleChirkut}{}{Personal Open-Source Project}{}
		\item A social network, built from scratch, for a better world.
		\item Available on Microsoft Store, Google Play, and as a Progressive Web Application.
	\end{rSubsection}

	\begin{rSubsection}{Bitscoper SSTV Icecast Broadcaster}{}{Personal Open-Source Project}{}
		\item A Python project that transmits images using 19 SSTV modes with VOX functionality through Icecast in Ogg Opus format with dynamic mount points.
	\end{rSubsection}

	\begin{rSubsection}{bitscoper.dev}{}{Personal Open-Source Project}{}
		\item A blog focused on Linux, server administration, computer history, and other technical topics. \\
	\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Strength}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} p{9cm} @{}}
		Programming Languages     & C, C++, Dart, PHP, JavaScript, Python				 \\
		Other Languages           & Bash, Nix, SQL, XHTML, CSS					         \\
		Frameworks                & Arduino, Flutter, Streamlit							 \\
		Containerization          & Docker, Podman										 \\
		VCS and CI/CD             & Git and GitHub Actions								 \\
		Database Server Softwares & PostgreSQL, MariaDB									 \\
		DNS Server Software       & BIND												 \\
		Web Server Softwares      & OpenLiteSpeed Web Server, NGINX, Hugo				 \\
		Mail Server Softwares     & Postfix, OpenDKIM, Dovecot							 \\
		Other Server Softwares    & Ollama, Icecast, MistServer, motionEye, Jellyfin	 \\
		Server Panel Softwares    & Cockpit, ISPConfig									 \\
		Virtualization            & KVM - QEMU											 \\
		Linux Distributions       & NixOS, AlmaLinux, Debian
	\end{tabular}

\end{rSection}

\begin{rSection}{Personal Information}

	\setlength{\LTleft}{12pt}

	\begin{longtable}{>{\bfseries}l @{\hspace{6ex}} p{9cm}}
		Father          & Dr. Md. Abdur Rahman Rakib    \\
		Mother          & Mst. Amena Khatun         	\\
		Date of Birth   & xxxxxxxx xx, xxxx         	\\
		Religion        & Islam                     	\\
		Nationality     & Bangladeshi               	\\
		Marrital Status & Unmarried                 	\\
		National ID     & xxxxxxxxx                 	\\
		GitHub          & github.com/bitscoper      	\\
		LinkedIn        & linkedin.com/in/bitscoper 	\\
		Website         & bitscoper.dev
	\end{longtable}

\end{rSection}

\begin{rSection}{Reference}

	\begin{multicols}{2}

		\textbf{Dr. Mohammad Shamsu Uddin}	\\
		Associate Professor				\\
		Department of BTM				\\
		IUT, OIC						\\
		Contact: msuddin@iut-dhaka.edu

		\columnbreak

		\textbf{Taslim Md. Khan}		\\
		Managing Director				\\
		AkijBashir Group				\\
		Dhaka, Bangladesh				\\
		Contact: taslim@akijbashir.com

	\end{multicols}

\end{rSection}

\end{document}